---
title: "dynclim — Specification Curves"
subtitle: "Multiverse & Cross-Validation Results by Industry and Outcome"
date: today
date-format: "MMMM D, YYYY"
author: "Mike"
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-location: left
    toc-title: "Contents"
    number-sections: true
    code-fold: true
    code-summary: "Show code"
    self-contained: true        # single portable file
    fig-align: center
    fig-width: 10
    fig-height: 6
    page-layout: full
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
# ============================================================
# CONFIGURATION — edit this block to match your file paths
# ============================================================

# Root directories for each industry's plot output
PLOT_DIRS <- list(
  rail = "rail_analysis/plots",
  nrc  = "nrc_analysis/plots"
)

# Outcomes for each industry.
# Each entry: list(id = "used_in_filename", label = "Human-readable label")
OUTCOMES <- list(
  rail = list(
    list(id = "hurdle_count",    label = "Event Count (Hurdle)"),
    list(id = "hurdle_severity", label = "Severity (Hurdle)")
  ),
  nrc = list(
    list(id = "ordinal_scram",   label = "Reactor Scram (Ordinal)"),
    list(id = "count_ler",       label = "LER Event Count")
  )
)

# Plot filename templates.
# Use {outcome} as the placeholder — it will be replaced with the outcome id.
# Adjust these to match what your R scripts actually save.
PLOT_TEMPLATES <- list(
  multiverse = "spec_curve_multiverse_{outcome}.png",
  cv         = "spec_curve_cv_{outcome}.png"
)

# ============================================================
# Helper functions — no need to edit below this line
# ============================================================

library(knitr)
library(glue)

plot_path <- function(industry, type, outcome_id) {
  dir      <- PLOT_DIRS[[industry]]
  template <- PLOT_TEMPLATES[[type]]
  fname    <- glue(template, outcome = outcome_id)
  file.path(dir, fname)
}

# Returns TRUE if file exists and is non-empty
plot_exists <- function(path) file.exists(path) && file.size(path) > 0

# Render one outcome section: multiverse + CV side by side
# Called inside a ::: panel-tabset block for each industry
render_outcome_section <- function(industry, outcome) {
  id    <- outcome$id
  label <- outcome$label

  mv_path <- plot_path(industry, "multiverse", id)
  cv_path <- plot_path(industry, "cv", id)

  cat(glue("\n\n### {label}\n\n"))
  cat("::: {.columns}\n\n")

  # Left column: multiverse
  cat("::: {.column width='50%'}\n")
  cat("**Multiverse Specification Curve**\n\n")
  if (plot_exists(mv_path)) {
    cat(glue("![]({mv_path}){{fig-alt='Multiverse spec curve for {label}' width=100%}}\n\n"))
  } else {
    cat(glue("> ⚠️ Plot not found: `{mv_path}`\n\n"))
  }
  cat(":::\n\n")

  # Right column: CV
  cat("::: {.column width='50%'}\n")
  cat("**Cross-Validation Specification Curve**\n\n")
  if (plot_exists(cv_path)) {
    cat(glue("![]({cv_path}){{fig-alt='CV spec curve for {label}' width=100%}}\n\n"))
  } else {
    cat(glue("> ⚠️ Plot not found: `{cv_path}`\n\n"))
  }
  cat(":::\n\n")

  cat(":::\n\n")
  cat("---\n\n")
}
```

## Overview {.unnumbered}

This document collects specification curves from the dynclim multiverse analysis across
all industries and outcomes. Each section contains the **multiverse** curve (all analytical
specifications ranked by effect size) alongside the **cross-validation** curve (same
specifications ranked by held-out Brier score) for direct comparison.

::: {.callout-note}
Plots are sourced directly from the R analysis output directories. Re-render this document
after any analysis run to update all figures automatically.
:::

## Rail {.tabset}

```{r rail-sections, results='asis'}
for (outcome in OUTCOMES$rail) {
  render_outcome_section("rail", outcome)
}
```

## NRC {.tabset}

```{r nrc-sections, results='asis'}
for (outcome in OUTCOMES$nrc) {
  render_outcome_section("nrc", outcome)
}
```
