---
title: "Multiverse Analysis — Executive Summary"
subtitle: "Dynamic Narrative Climate Toolkit"
author: "Generated by dynclim"
date: today
format:
  pdf:
    toc: true
    toc-depth: 2
    number-sections: true
    colorlinks: true
    fig-pos: "H"
    geometry:
      - top=1in
      - bottom=1in
      - left=0.75in
      - right=0.75in
    header-includes:
      - \usepackage{booktabs}
      - \usepackage{longtable}
      - \usepackage{float}
      - \usepackage{pdflscape}
      - \floatplacement{figure}{H}
params:
  figure_dir: "report_figures"
  manifest: "report_figures/_manifest.csv"
  industry_labels: "rail=Rail (FRA);nrc=Nuclear (NRC)"
  track: "event"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  out.width = "100%"
)

library(tidyverse)
library(knitr)
library(kableExtra)

manifest <- read_csv(params$manifest, show_col_types = FALSE)

parse_labels <- function(label_str) {
  pairs  <- str_split(label_str, ";")[[1]]
  parsed <- str_split(pairs, "=", n = 2)
  setNames(
    sapply(parsed, function(x) if (length(x) > 1) x[2] else x[1]),
    sapply(parsed, function(x) x[1])
  )
}

industry_labels <- parse_labels(params$industry_labels)
figure_dir <- params$figure_dir
cross_dir  <- file.path(figure_dir, "_cross_industry")

escape_latex <- function(x) {
  x <- gsub("\\\\", "\\\\textbackslash{}", x)
  x <- gsub("([#$%&_{}])", "\\\\\\1", x)
  x <- gsub("~", "\\\\textasciitilde{}", x)
  x <- gsub("\\^", "\\\\textasciicircum{}", x)
  x
}

emit_figure <- function(path, caption, width = "\\textwidth") {
  if (!file.exists(path)) {
    alt <- file.path(figure_dir, basename(path))
    if (file.exists(alt)) path <- alt
    else {
      cat(sprintf("\n\n\\textit{[Figure not found: %s]}\n\n", escape_latex(basename(path))))
      return(invisible(NULL))
    }
  }
  abs_path <- normalizePath(path, mustWork = FALSE)
  cat(sprintf(
    "\n\n\\begin{figure}[H]\n\\centering\n\\includegraphics[width=%s]{%s}\n\\caption{%s}\n\\end{figure}\n\n",
    width, abs_path, escape_latex(caption)
  ))
}

industries_in_manifest <- if ("industry" %in% names(manifest)) {
  unique(manifest$industry[manifest$industry != "_cross_industry"])
} else character(0)
```

# Overview

Executive summary of the panel-rate multiverse and cross-validation analyses
across `r length(industries_in_manifest)` industry domain(s):
`r paste(sapply(industries_in_manifest, function(x) industry_labels[x] %||% x), collapse = ", ")`.

For each industry × outcome × CV strategy, the analysis sweeps every
climate-config × climate-window combination (typically ~800 specifications)
through a panel-rate generalized linear mixed model. CV held-out log-likelihood
is computed against a strong "seasonal + ops" baseline to identify
specifications where climate features add predictive value. The
"candidate-champion pool" comprises specifications within 10% of the best
delta-loglik per cell.

This summary covers five sections:

1. Cross-industry robustness summary
2. Configuration importance across industries
3. Climate vs. operational effects (champion-filtered)
4. Spec curves per outcome
5. Single best specification + facet enrichment

The full report (`mv_report_panel_full.pdf`) contains per-industry
sections with all CV figures, full robustness tables, and per-outcome
diagnostics.

\newpage

# 1. Cross-Industry Robustness Summary

Climate-effect distribution across the multiverse, summarized per
(industry × outcome × component × specification set). The "% Negative"
column captures the direction of the climate effect across the multiverse;
the "% Sig." column captures statistical significance at p < 0.05.

```{r robustness, results='asis'}
rob_path <- file.path(cross_dir, "cross_industry_robustness.csv")
if (file.exists(rob_path)) {
  rob <- read_csv(rob_path, show_col_types = FALSE)
  if (nrow(rob) > 0) {
    cat("\\begin{landscape}\n")
    rob_tbl <- rob %>%
      mutate(across(where(is.numeric), ~ round(., 2))) %>%
      kable(
        format = "latex",
        booktabs = TRUE,
        longtable = TRUE,
        col.names = c("Industry", "Outcome", "Component", "Spec. Set",
                       "N", "Mean Est.", "SD Est.", "Median Est.",
                       "\\% Sig.", "\\% Neg.", "\\% Neg. Sig."),
        escape = FALSE,
        caption = "Cross-industry robustness summary."
      ) %>%
      kable_styling(latex_options = c("hold_position", "repeat_header"),
                    font_size = 10)
    print(rob_tbl)
    cat("\\end{landscape}\n\n")
  }
}
```

\newpage

# 2. Configuration Importance Across Industries

Variance in the climate effect estimate explained by each analytical choice
(univariate $R^2$ from a one-way ANOVA per facet × outcome). Larger bars
indicate analytical choices that systematically shift the climate effect —
i.e., where the methodology is sensitive to the choice.

```{r config-importance, results='asis'}
imp_fig <- list.files(cross_dir, pattern = "config_importance_comparison",
                       full.names = TRUE)
if (length(imp_fig) > 0) {
  emit_figure(imp_fig[1],
              "Configuration importance across industries.",
              width = "\\textwidth")
}

imp_csv <- file.path(cross_dir, "cross_industry_importance.csv")
if (file.exists(imp_csv)) {
  imp <- read_csv(imp_csv, show_col_types = FALSE)
  if (nrow(imp) > 0) {
    # Show only the per-industry × per-outcome top variable to keep the
    # table readable. Pulls the highest-pct_variance row per group.
    top_per_cell <- imp %>%
      filter(!is.na(pct_variance)) %>%
      group_by(industry_label, outcome_label) %>%
      slice_max(pct_variance, n = 3, with_ties = FALSE) %>%
      ungroup() %>%
      mutate(across(where(is.numeric), ~ round(., 2))) %>%
      select(industry_label, outcome_label, var_label,
             pct_variance, p_value, significance)

    cat("\\begin{landscape}\n")
    tbl <- top_per_cell %>%
      kable(format = "latex", booktabs = TRUE, longtable = TRUE,
            col.names = c("Industry", "Outcome", "Variable",
                          "\\% Variance", "p-value", "Sig."),
            escape = FALSE,
            caption = paste0("Top 3 most-important analytical choices per ",
                             "industry × outcome.")) %>%
      kable_styling(latex_options = c("hold_position", "repeat_header"),
                    font_size = 9)
    print(tbl)
    cat("\\end{landscape}\n\n")
  }
}
```

\newpage

# 3. Climate vs. Operational Effects — Champion-Filtered

Effect-size comparison between the climate score and operational covariates,
restricted to **candidate-champion specifications only** — i.e., specs
within 10% of the best CV delta-loglik per (industry × outcome × CV strategy).
This focuses on the configurations that demonstrably forecast safety
outcomes, dropping the multiverse "noise floor."

```{r climate-vs-ops, results='asis'}
ops_fig_champ <- list.files(cross_dir,
                             pattern = "climate_vs_ops_comparison_champions",
                             full.names = TRUE)
if (length(ops_fig_champ) > 0) {
  cat("\\begin{landscape}\n")
  emit_figure(ops_fig_champ[1],
              "Climate vs. operational effects across industries (champion-filtered).",
              width = "\\textwidth")
  cat("\\end{landscape}\n\n")
} else {
  # Fallback to CV-filtered if the champion-filtered figure isn't available
  ops_fig <- list.files(cross_dir,
                         pattern = "climate_vs_ops_comparison_filtered",
                         full.names = TRUE)
  if (length(ops_fig) > 0) {
    cat("\\begin{landscape}\n")
    emit_figure(ops_fig[1],
                "Climate vs. operational effects across industries (CV-filtered).",
                width = "\\textwidth")
    cat("\\end{landscape}\n\n")
  }
}
```

\newpage

# 4. Spec Curves Per Outcome

Specification curves for each (industry × outcome). Each plot orders the
~800 multiverse specifications by climate-effect estimate; tile strips
beneath show which analytical choices drive movement up or down the curve.

```{r spec-curves, results='asis'}
# Collect every spec_curve figure across industries and emit them four-up.
# Each industry directory holds files named like
# rate_<outcome>[_filtered]_spec_curve.pdf -- exclude the _filtered ones from
# this section since the executive summary uses unfiltered curves only.
all_spec_pdfs <- character(0)
for (ind in industries_in_manifest) {
  ind_dir <- file.path(figure_dir, ind)
  if (!dir.exists(ind_dir)) next
  pdfs <- list.files(ind_dir, pattern = "_spec_curve\\.pdf$", full.names = TRUE)
  pdfs <- pdfs[!grepl("_filtered_spec_curve\\.pdf$", pdfs)]
  if (length(pdfs) > 0) {
    pdfs <- setNames(pdfs, paste0(ind, ":", basename(pdfs)))
    all_spec_pdfs <- c(all_spec_pdfs, pdfs)
  }
}

if (length(all_spec_pdfs) > 0) {
  # Emit two-up using the LaTeX subfigure pattern; \includegraphics at half
  # textwidth and pair them via minipages so two compact curves sit on one
  # row. Spec curves are tall, so two per row is the readable max.
  cat("Each pair below represents one (industry, outcome). Two pairs per ",
      "page; specifications ordered by climate-effect estimate. ",
      "Tile-strip panels beneath each curve show which analytical choices ",
      "(window type/size, lag, embedding model, sentiment method, composite ",
      "method) appear at each rank — over-represented patterns are visible ",
      "as colored bands.\n\n", sep = "")
  for (i in seq_along(all_spec_pdfs)) {
    path <- all_spec_pdfs[i]
    label_parts <- str_split(names(all_spec_pdfs)[i], ":")[[1]]
    ind_key <- label_parts[1]
    fname   <- label_parts[2]
    outcome_clean <- fname %>%
      str_remove("_spec_curve\\.pdf$") %>%
      str_replace_all("_", " ") %>%
      tools::toTitleCase()
    ind_lab <- industry_labels[ind_key] %||% toupper(ind_key)
    emit_figure(path,
                sprintf("%s -- %s.", ind_lab, outcome_clean),
                width = "0.85\\textwidth")
    if (i %% 2 == 0) cat("\\clearpage\n")
  }
}
```

\newpage

# 5. Single Best Specification + Facet Enrichment

The best-performing specification per (industry × outcome × CV strategy),
together with which analytical choices systematically appear in the
candidate-champion pool. "Lift" is $\log_2(\text{top share / all share})$;
$q$ is BH-FDR-adjusted within each cell.

```{r champions, results='asis'}
xi_path <- file.path(cross_dir, "cross_industry_champion_rollup.csv")
if (file.exists(xi_path)) {
  xi <- read_csv(xi_path, show_col_types = FALSE)
  if (nrow(xi) > 0) {
    cat("\n\n## Cross-Industry Facet Dominance\n\n")
    cat("How often each analytical choice dominates the candidate-champion ",
        "pool across all (industry × outcome × CV strategy) cells. ",
        "High `cells_dominated` indicates the choice systematically wins.\n\n",
        sep = "")
    tbl <- xi %>%
      kable(format = "latex", booktabs = TRUE, longtable = TRUE,
            col.names = c("Facet", "Dominant Level", "Cells Dominated",
                          "Total Cells", "% Dominated"),
            caption = "Cross-industry dominance counts.") %>%
      kable_styling(latex_options = c("hold_position", "repeat_header",
                                       "scale_down"),
                    font_size = 9)
    print(tbl)
    cat("\n\n")
  }
}

# Per-industry: best spec table + filtered facet enrichment
champ_paths <- list.files(figure_dir, pattern = "^champions_best\\.csv$",
                           recursive = TRUE, full.names = TRUE)
for (cp in champ_paths) {
  ind_key   <- basename(dirname(cp))
  ind_label <- industry_labels[ind_key] %||% toupper(ind_key)
  best <- read_csv(cp, show_col_types = FALSE)
  enrich_path <- file.path(dirname(cp), "champions_facet_enrichment.csv")

  cat(sprintf("\n\n## %s\n\n", ind_label))

  if (nrow(best) > 0) {
    cat("\n\n### Single Best Specification\n\n")
    cat("\\begin{landscape}\n")
    keep_cols <- intersect(c("outcome", "cv_strategy", "best_config_id",
                              "best_delta_ll",
                              "climate_estimate", "climate_pval",
                              "embedding_model", "sent_method",
                              "comp__method",
                              "window_type", "window_size",
                              "lag_days", "halflife_days"),
                            names(best))
    best_clean <- best %>% select(any_of(keep_cols)) %>%
      mutate(across(where(is.numeric), ~ round(., 4)))
    tbl <- best_clean %>%
      kable(format = "latex", booktabs = TRUE, longtable = TRUE,
            caption = sprintf("%s: best spec per (outcome x CV strategy).",
                               ind_label)) %>%
      kable_styling(latex_options = c("hold_position", "repeat_header"),
                     font_size = 9)
    print(tbl)
    cat("\\end{landscape}\n\n")
  }

  if (file.exists(enrich_path)) {
    enrich <- read_csv(enrich_path, show_col_types = FALSE)
    if (nrow(enrich) > 0) {
      flagged <- enrich %>%
        filter(top_n >= 1L,
               (!is.na(q_value) & q_value < 0.10) | enrichment > 0.5) %>%
        arrange(outcome, cv_strategy, desc(enrichment))

      if (nrow(flagged) > 0) {
        cat("\n\n### Notable Facet Enrichment\n\n")
        flagged_clean <- flagged %>%
          mutate(across(where(is.numeric), ~ round(., 4))) %>%
          mutate(across(c(outcome, cv_strategy, facet, level),
                        ~ gsub("_", "\\\\_", as.character(.x)))) %>%
          select(outcome, cv_strategy, facet, level, top_n, top_share,
                 all_share, enrichment, p_value, q_value)
        cat("\\begin{landscape}\n")
        tbl <- flagged_clean %>%
          kable(format = "latex", booktabs = TRUE, longtable = TRUE,
                col.names = c("Outcome", "CV", "Facet", "Level",
                              "Top n", "Top \\%", "All \\%",
                              "Lift (log2)", "p", "q (FDR)"),
                escape = FALSE,
                caption = sprintf("%s: facet enrichment in champion pool.",
                                   ind_label)) %>%
          kable_styling(latex_options = c("hold_position", "repeat_header"),
                         font_size = 9)
        print(tbl)
        cat("\\end{landscape}\n\n")
      }
    }
  }
}
```
