---
title: "Multiverse Analysis Report"
subtitle: "Dynamic Narrative Climate Toolkit -- Study Team Review"
author: "Generated by dynclim"
date: today
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    colorlinks: true
    fig-pos: "H"
    geometry:
      - top=1in
      - bottom=1in
      - left=0.75in
      - right=0.75in
    header-includes:
      - \usepackage{booktabs}
      - \usepackage{longtable}
      - \usepackage{float}
      - \usepackage{pdflscape}
      - \floatplacement{figure}{H}
params:
  figure_dir: "report_figures"
  manifest: "report_figures/_manifest.csv"
  industry_labels: "rail=Rail (FRA);nrc=Nuclear (NRC)"
  track: "event"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  out.width = "100%"
)

library(tidyverse)
library(knitr)
library(kableExtra)

# Load manifest
manifest <- read_csv(params$manifest, show_col_types = FALSE)

# Parse industry labels
parse_labels <- function(label_str) {
  pairs <- str_split(label_str, ";")[[1]]
  parsed <- str_split(pairs, "=", n = 2)
  setNames(
    sapply(parsed, function(x) if (length(x) > 1) x[2] else x[1]),
    sapply(parsed, function(x) x[1])
  )
}

industry_labels <- parse_labels(params$industry_labels)
figure_dir <- params$figure_dir

# Helper: escape LaTeX special characters in captions
escape_latex <- function(x) {
  x <- gsub("\\\\", "\\\\textbackslash{}", x)
  x <- gsub("([#$%&_{}])", "\\\\\\1", x)
  x <- gsub("~", "\\\\textasciitilde{}", x)
  x <- gsub("\\^", "\\\\textasciicircum{}", x)
  x
}

# Helper: emit a figure via raw LaTeX cat()
emit_figure <- function(path, caption, width = "\\textwidth") {
  # Try the path as-is first, then try relative to figure_dir
  if (!file.exists(path)) {
    # The manifest may have relative paths — try resolving from figure_dir
    alt_path <- file.path(figure_dir, basename(path))
    if (file.exists(alt_path)) {
      path <- alt_path
    } else {
      cat(sprintf("\n\n\\textit{[Figure not found: %s]}\n\n", escape_latex(basename(path))))
      return(invisible(NULL))
    }
  }
  # LaTeX needs absolute paths
  abs_path <- normalizePath(path, mustWork = FALSE)
  safe_caption <- escape_latex(caption)
  cat(sprintf(
    "\n\n\\begin{figure}[H]\n\\centering\n\\includegraphics[width=%s]{%s}\n\\caption{%s}\n\\end{figure}\n\n",
    width, abs_path, safe_caption
  ))
}

# Helper: read and format a robustness CSV as kable
show_robustness <- function(ind, out, comp) {
  comp_part <- if (comp != "single") paste0("_", comp) else ""
  csv_path <- file.path(figure_dir, ind, paste0(out, comp_part, "_robustness.csv"))
  if (!file.exists(csv_path)) return(invisible(NULL))

  is_filtered <- grepl("_filtered$", out)
  base_out <- sub("_filtered$", "", out)
  out_display <- tools::toTitleCase(gsub("_", " ", base_out))
  filter_tag <- if (is_filtered) " [CV-Filtered]" else ""
  comp_tag <- if (comp != "single") paste0(" (", comp, ")") else ""

  rob <- read_csv(csv_path, show_col_types = FALSE)
  rob %>%
    mutate(across(where(is.numeric), ~round(., 2))) %>%
    kable(
      format = "latex",
      booktabs = TRUE,
      caption = sprintf("Robustness summary: %s%s%s",
                        out_display, comp_tag, filter_tag)
    ) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}

# Helper: read and format config importance CSV as kable
show_importance_table <- function(ind, out, comp) {
  comp_part <- if (comp != "single") paste0("_", comp) else ""
  csv_path <- file.path(figure_dir, ind, paste0(out, comp_part, "_config_importance.csv"))
  if (!file.exists(csv_path)) return(invisible(NULL))

  imp <- read_csv(csv_path, show_col_types = FALSE)
  imp %>%
    select(variable, pct_variance, f_statistic, p_value, significance, n_levels) %>%
    mutate(
      variable = variable %>%
        str_replace_all("__", ": ") %>%
        str_replace_all("_", " ") %>%
        tools::toTitleCase(),
      across(c(pct_variance, f_statistic, p_value), ~round(., 3))
    ) %>%
    kable(
      format = "latex",
      booktabs = TRUE,
      col.names = c("Variable", "\\% Var. Explained", "F", "p", "Sig.", "Levels"),
      escape = FALSE,
      caption = sprintf("Configuration importance: %s %s",
                        tools::toTitleCase(gsub("_", " ", out)),
                        if (comp != "single") paste0("(", comp, ")") else "")
    ) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}

# Organize the manifest for iteration — exclude cross-industry summary entries
industries_in_manifest <- unique(manifest$industry)
industries_in_manifest <- industries_in_manifest[!grepl("^_", industries_in_manifest)]
```

# Overview

This report presents the multiverse analysis results across `r length(industries_in_manifest)` industry domain(s): `r paste(sapply(industries_in_manifest, function(x) industry_labels[x] %||% x), collapse = ", ")`. For each outcome within each industry, the following diagnostics are presented:

1. **Specification curve** -- Climate effect estimates sorted by magnitude, with decision indicator panels showing which analytical choices drive the result.
2. **Configuration importance** -- Variance decomposition showing which analytical choices (embedding model, sentiment model, composite method, window parameters) explain the most variation in the climate effect.
3. **Climate vs. operational comparison** -- Side-by-side effect sizes for the climate score versus operational covariates.
4. **Cross-validation** -- `r if (params$track == "panel") "Held-out log-likelihood specification curves and delta-log-lik plots" else "Brier score specification curves and delta-Brier plots"` (where CV results are available).

\newpage

```{r cross-industry, results='asis'}
# Cross-industry summary section — only renders if 2+ industries
cross_dir <- file.path(figure_dir, "_cross_industry")
has_cross <- dir.exists(cross_dir)

if (has_cross && length(industries_in_manifest) >= 2) {

  cat("\n\n# Cross-Industry Summary\n\n")

  # Robustness comparison table
  rob_path <- file.path(cross_dir, "cross_industry_robustness.csv")
  if (file.exists(rob_path)) {
    rob <- read_csv(rob_path, show_col_types = FALSE)
    cat("\n\n## Robustness Comparison\n\n")
    cat("Summary of climate effect robustness across all industries, outcomes, and model components.\n\n")

    cat("\\begin{landscape}\n")
    rob_tbl <- rob %>%
      mutate(across(where(is.numeric), ~round(., 2))) %>%
      kable(
        format = "latex",
        booktabs = TRUE,
        longtable = TRUE,
        col.names = c("Industry", "Outcome", "Component", "Spec. Set",
                       "N", "Mean Est.", "SD Est.", "Median Est.",
                       "\\% Sig.", "\\% Neg.", "\\% Neg. Sig."),
        escape = FALSE,
        caption = "Cross-industry robustness summary. Spec.\\ Set: All = full multiverse; CV-Filtered = only specifications where climate improves out-of-sample prediction."
      ) %>%
      kable_styling(latex_options = c("hold_position", "repeat_header"),
                    font_size = 10)
    print(rob_tbl)
    cat("\\end{landscape}\n\n")
  }

  # Config importance comparison plot
  imp_fig <- list.files(cross_dir, pattern = "config_importance_comparison",
                        full.names = TRUE)
  if (length(imp_fig) > 0) {
    cat("\n\n## Configuration Importance Comparison\n\n")
    cat("Comparison of which analytical choices (embedding model, sentiment method, composite method, window parameters) drive the most variance in climate effect estimates across industries and outcomes.\n\n")
    emit_figure(imp_fig[1],
                "Configuration importance comparison across industries",
                width = "\\textwidth")
  }

  # Climate vs ops comparison plots (unfiltered and filtered)
  ops_fig_unfiltered <- list.files(cross_dir,
                                    pattern = "climate_vs_ops_comparison\\.pdf$",
                                    full.names = TRUE)
  ops_fig_filtered <- list.files(cross_dir,
                                  pattern = "climate_vs_ops_comparison_filtered",
                                  full.names = TRUE)

  if (length(ops_fig_unfiltered) > 0 || length(ops_fig_filtered) > 0) {
    cat("\n\n## Climate vs. Operational Effects Comparison\n\n")
    cat("Side-by-side comparison of climate score effects relative to operational covariates across industries. Note that operational variables differ by industry.\n\n")
  }

  if (length(ops_fig_unfiltered) > 0) {
    cat("\\begin{landscape}\n")
    emit_figure(ops_fig_unfiltered[1],
                "Climate vs. operational effects across industries (all specifications)",
                width = "\\textwidth")
    cat("\\end{landscape}\n\n")
  }

  if (length(ops_fig_filtered) > 0) {
    cat("\n\n**CV-Filtered** *(only specifications where climate improves out-of-sample prediction)*\n\n")
    cat("\\begin{landscape}\n")
    emit_figure(ops_fig_filtered[1],
                "Climate vs. operational effects across industries (CV-filtered)",
                width = "\\textwidth")
    cat("\\end{landscape}\n\n")
  }

  cat("\n\n\\newpage\n\n")
}
```

```{r body, results='asis'}
for (ind in industries_in_manifest) {

  ind_label <- industry_labels[ind] %||% toupper(ind)
  cat(sprintf("\n\n# %s\n\n", ind_label))

  # Get outcomes for this industry — separate unfiltered from filtered
  ind_manifest <- manifest %>% filter(industry == ind)
  all_outcomes <- unique(ind_manifest$outcome)
  filtered_outcomes <- all_outcomes[grepl("_filtered$", all_outcomes)]
  base_outcomes <- all_outcomes[!grepl("_filtered$", all_outcomes)]

  # Check if CV filter stats exist for this industry
  filter_stats_path <- file.path(figure_dir, ind, "cv_filter_stats.csv")
  has_filtering <- length(filtered_outcomes) > 0

  if (has_filtering && file.exists(filter_stats_path)) {
    fs <- read_csv(filter_stats_path, show_col_types = FALSE)
    cat(sprintf("\n\n*CV pre-filtering applied: %d/%d specifications retained (%.1f%%) using '%s' baseline.*\n\n",
                fs$n_credible[1], fs$n_total[1], fs$pct_retained[1], fs$baseline_strategy[1]))
  }

  for (out in base_outcomes) {

    out_label <- tools::toTitleCase(gsub("_", " ", out))
    out_filtered <- paste0(out, "_filtered")
    has_filtered <- out_filtered %in% filtered_outcomes

    cat(sprintf("\n\n## %s\n\n", out_label))

    # Get components for this outcome
    out_manifest <- ind_manifest %>% filter(outcome == out)

    # Separate MV components from CV strategies
    mv_components <- out_manifest %>%
      filter(figure_type %in% c("spec_curve", "config_importance", "climate_vs_ops")) %>%
      pull(component) %>% unique()

    cv_components <- out_manifest %>%
      filter(figure_type %in% c("cv_brier_spec", "delta_brier",
                                "cv_loglik_spec", "delta_loglik")) %>%
      pull(component) %>% unique()

    # --- MV figures per component ---
    for (comp in mv_components) {

      comp_label <- dplyr::case_when(
        comp == "cond"   ~ "Conditional Component",
        comp == "zi"     ~ "Zero-Inflation Component",
        comp == "single" ~ "",
        TRUE             ~ comp
      )

      if (comp_label != "") {
        cat(sprintf("\n\n### %s\n\n", comp_label))
      }

      # Robustness table
      rob_tbl <- show_robustness(ind, out, comp)
      if (!is.null(rob_tbl)) {
        cat("\n\n")
        print(rob_tbl)
        cat("\n\n")
      }

      # Spec curve
      spec_row <- out_manifest %>%
        filter(component == comp, figure_type == "spec_curve")
      if (nrow(spec_row) > 0) {
        emit_figure(spec_row$path[1],
                    paste("Specification curve:", out_label, comp_label))
      }

      # Config importance bar chart
      imp_row <- out_manifest %>%
        filter(component == comp, figure_type == "config_importance")
      if (nrow(imp_row) > 0) {
        emit_figure(imp_row$path[1],
                    paste("Configuration importance:", out_label, comp_label),
                    width = "0.85\\textwidth")
      }

      # Config importance table
      imp_tbl <- show_importance_table(ind, out, comp)
      if (!is.null(imp_tbl)) {
        cat("\n\n")
        print(imp_tbl)
        cat("\n\n")
      }

      # Climate vs ops
      ops_row <- out_manifest %>%
        filter(component == comp, figure_type == "climate_vs_ops")
      if (nrow(ops_row) > 0) {
        emit_figure(ops_row$path[1],
                    paste("Climate vs. operational effects:", out_label, comp_label),
                    width = "0.9\\textwidth")
      }

      # --- CV-FILTERED versions (if available) ---
      if (has_filtered) {
        filt_manifest <- ind_manifest %>% filter(outcome == out_filtered)
        filt_for_comp <- filt_manifest %>%
          filter(component == comp,
                 figure_type %in% c("spec_curve", "config_importance", "climate_vs_ops"))

        if (nrow(filt_for_comp) > 0) {
          # Use a visually distinct subsection heading so filtered results stand out
          filt_heading <- if (comp_label != "") {
            sprintf("CV-Filtered Results: %s %s", out_label, comp_label)
          } else {
            sprintf("CV-Filtered Results: %s", out_label)
          }
          cat(sprintf("\n\n#### %s\n\n", filt_heading))
          cat("*Only specifications where adding climate variables improves out-of-sample prediction (delta-Brier < 0).*\n\n")

          # Filtered robustness
          rob_filt <- show_robustness(ind, out_filtered, comp)
          if (!is.null(rob_filt)) {
            cat("\n\n")
            print(rob_filt)
            cat("\n\n")
          }

          # Filtered spec curve
          spec_filt <- filt_manifest %>%
            filter(component == comp, figure_type == "spec_curve")
          if (nrow(spec_filt) > 0) {
            emit_figure(spec_filt$path[1],
                        paste("Specification curve [CV-Filtered]:", out_label, comp_label))
          }

          # Filtered config importance
          imp_filt <- filt_manifest %>%
            filter(component == comp, figure_type == "config_importance")
          if (nrow(imp_filt) > 0) {
            emit_figure(imp_filt$path[1],
                        paste("Configuration importance [CV-Filtered]:", out_label, comp_label),
                        width = "0.85\\textwidth")
          }

          # Filtered climate vs ops
          ops_filt <- filt_manifest %>%
            filter(component == comp, figure_type == "climate_vs_ops")
          if (nrow(ops_filt) > 0) {
            emit_figure(ops_filt$path[1],
                        paste("Climate vs. operational effects [CV-Filtered]:", out_label, comp_label),
                        width = "0.9\\textwidth")
          }
        }
      }

    }  # end MV component loop

    # --- CV figures ---
    if (length(cv_components) > 0) {
      cat("\n\n### Cross-Validation\n\n")

      for (cv_comp in cv_components) {

        cv_label <- dplyr::case_when(
          cv_comp == "group_kfold" ~ "Group K-Fold",
          cv_comp == "timeseries"  ~ "Time-Series",
          TRUE                     ~ cv_comp
        )

        cat(sprintf("\n\n#### %s\n\n", cv_label))

        # CV spec curve (Brier for event track, log-lik for panel track)
        spec_type <- if (params$track == "panel") "cv_loglik_spec" else "cv_brier_spec"
        spec_caption <- if (params$track == "panel") "CV log-likelihood:" else "CV Brier scores:"
        brier_row <- out_manifest %>%
          filter(component == cv_comp, figure_type == spec_type)
        if (nrow(brier_row) > 0) {
          emit_figure(brier_row$path[1],
                      paste(spec_caption, out_label, "--", cv_label))
        }

        # Delta plot
        delta_type <- if (params$track == "panel") "delta_loglik" else "delta_brier"
        delta_caption <- if (params$track == "panel") "Delta-log-lik:" else "Delta-Brier:"
        delta_row <- out_manifest %>%
          filter(component == cv_comp, figure_type == delta_type)
        if (nrow(delta_row) > 0) {
          emit_figure(delta_row$path[1],
                      paste(delta_caption, out_label, "--", cv_label))
        }
      }
    }

    cat("\n\n\\newpage\n\n")

  }  # end outcome loop
}  # end industry loop
```

```{r champion-models-appendix, results='asis'}
# Champion Models — single best spec per (outcome × cv_strategy), candidate
# pool within 10% of best, and facet-level enrichment in that pool. Reads
# CSVs written by best_model_analysis.R via generate_industry_figures().
champ_paths <- list.files(figure_dir, pattern = "^champions_best\\.csv$",
                           recursive = TRUE, full.names = TRUE)
xi_path <- file.path(figure_dir, "_cross_industry",
                     "cross_industry_champion_rollup.csv")
if (length(champ_paths) > 0) {
  cat("\n\n# Champion Models\n\n")
  cat("For each industry × outcome × CV strategy, the single best ",
      "specification (highest delta-loglik vs the seasonal+ops baseline) is ",
      "called out. The 'candidate champion pool' includes any specification ",
      "within 10% of the best — used to identify which analytical choices ",
      "(embedding model, sentiment method, composite method, climate window) ",
      "systematically appear in winning configurations.\n\n", sep = "")

  # Cross-industry roll-up first — the headline summary
  if (file.exists(xi_path)) {
    xi <- read_csv(xi_path, show_col_types = FALSE)
    if (nrow(xi) > 0) {
      cat("\n\n## Cross-Industry: Dominant Facet Levels\n\n")
      cat("Across all (industry × outcome × CV strategy) cells, this counts ",
          "how often each level dominates the candidate-champion pool. ",
          "High `cells_dominated` for a level suggests that choice ",
          "systematically wins.\n\n", sep = "")
      tbl <- xi %>%
        kable(format = "latex", booktabs = TRUE, longtable = TRUE,
              col.names = c("Facet", "Dominant Level", "Cells Dominated",
                            "Total Cells", "% Dominated"),
              caption = "Cross-industry facet dominance among candidate champions.") %>%
        kable_styling(latex_options = c("hold_position", "repeat_header",
                                          "scale_down"),
                       font_size = 9)
      print(tbl)
      cat("\n\n")
    }
  }

  # Per-industry: best-spec callouts + facet enrichment
  for (cp in champ_paths) {
    ind_key <- basename(dirname(cp))
    ind_label <- industry_labels[ind_key] %||% toupper(ind_key)
    best <- read_csv(cp, show_col_types = FALSE)
    diag_path <- file.path(dirname(cp), "champions_diagnostics.csv")
    enrich_path <- file.path(dirname(cp), "champions_facet_enrichment.csv")

    cat(sprintf("\n\n## %s\n\n", ind_label))

    # Best spec table — landscape because of column count.
    # Drop best_climate_var (redundant with parsed window facets), th__method
    # (often missing), and shorten the climate-effect columns to save space.
    if (nrow(best) > 0) {
      cat("\n\n### Single Best Specification\n\n")
      cat("\\begin{landscape}\n")
      keep_cols <- intersect(c("outcome", "cv_strategy", "best_config_id",
                                "best_delta_ll",
                                "climate_estimate", "climate_pval",
                                "embedding_model", "sent_method",
                                "comp__method",
                                "window_type", "window_size",
                                "lag_days", "halflife_days"),
                              names(best))
      best_clean <- best %>% select(any_of(keep_cols)) %>%
        mutate(across(where(is.numeric), ~ round(., 4)))
      tbl <- best_clean %>%
        kable(format = "latex", booktabs = TRUE, longtable = TRUE,
              caption = sprintf("%s: best spec per (outcome x CV strategy).",
                                 ind_label)) %>%
        kable_styling(latex_options = c("hold_position", "repeat_header"),
                       font_size = 9)
      print(tbl)
      cat("\\end{landscape}\n\n")
    }

    # Candidate-pool diagnostics
    if (file.exists(diag_path)) {
      diag <- read_csv(diag_path, show_col_types = FALSE)
      if (nrow(diag) > 0) {
        cat("\n\n### Candidate Champion Pool Sizes\n\n")
        diag_clean <- diag %>%
          mutate(across(where(is.numeric), ~ round(., 4)))
        tbl <- diag_clean %>%
          kable(format = "latex", booktabs = TRUE,
                caption = sprintf("%s: number of specs within 10%% of the best.",
                                   ind_label)) %>%
          kable_styling(latex_options = c("hold_position"), font_size = 9)
        print(tbl)
        cat("\n\n")
      }
    }

    # Facet enrichment — only show meaningful ones (q < 0.1 OR |enrichment| > 1)
    if (file.exists(enrich_path)) {
      enrich <- read_csv(enrich_path, show_col_types = FALSE)
      if (nrow(enrich) > 0) {
        # Show only levels that actually appear in the candidate pool
        # (top_n >= 1) — the absence of a level is implicit by complement,
        # and would otherwise generate large negative-enrichment rows that
        # mirror the positive ones.
        flagged <- enrich %>%
          filter(top_n >= 1L,
                 (!is.na(q_value) & q_value < 0.10) | enrichment > 0.5) %>%
          arrange(outcome, cv_strategy, desc(enrichment))

        if (nrow(flagged) > 0) {
          cat("\n\n### Facet Enrichment in Candidate Pool\n\n")
          cat("Facet levels over-represented in the candidate champion pool ",
              "relative to the full multiverse. Enrichment is ",
              "log2(top\\_share / all\\_share); q is BH-FDR-adjusted within ",
              "each cell. Filtered to: top\\_n $\\geq$ 1 AND ",
              "(q $<$ 0.10 OR enrichment $>$ 0.5).\n\n", sep = "")
          # Escape underscores in text cells (outcome/cv_strategy/facet/level
          # contain identifiers like "rate_emerg" / "comp__method" that LaTeX
          # would interpret as math-mode subscripts). Keep escape=FALSE for
          # the col.names so we can use \\% etc.
          flagged_clean <- flagged %>%
            mutate(across(where(is.numeric), ~ round(., 4))) %>%
            mutate(across(c(outcome, cv_strategy, facet, level),
                          ~ gsub("_", "\\\\_", as.character(.x)))) %>%
            select(outcome, cv_strategy, facet, level, top_n, top_share,
                   all_share, enrichment, p_value, q_value)
          cat("\\begin{landscape}\n")
          tbl <- flagged_clean %>%
            kable(format = "latex", booktabs = TRUE, longtable = TRUE,
                  col.names = c("Outcome", "CV", "Facet", "Level",
                                "Top n", "Top \\%", "All \\%",
                                "Lift (log2)", "p", "q (FDR)"),
                  escape = FALSE,
                  caption = sprintf("%s: notable facet enrichment.",
                                     ind_label)) %>%
            kable_styling(latex_options = c("hold_position", "repeat_header"),
                           font_size = 9)
          print(tbl)
          cat("\\end{landscape}\n\n")
        }
      }
    }
  }
  cat("\n\n\\newpage\n\n")
}
```

```{r model-details-appendix, results='asis'}
# Model details appendix — populated only for panel track.
# Reads per-industry model_details.csv (written by generate_industry_figures()
# when track == "panel") and renders one kable per industry.
if (params$track == "panel") {
  md_paths <- list.files(figure_dir, pattern = "^model_details\\.csv$",
                          recursive = TRUE, full.names = TRUE)
  if (length(md_paths) > 0) {
    cat("\n\n# Appendix: Model Details (Panel Track)\n\n")
    cat("Per-outcome family choice, sample size, and (where applicable) ",
        "Tweedie variance-power parameter $p$ across the multiverse. ",
        "$p \\in (1, 2)$ implies a compound Poisson-Gamma; ",
        "$p \\to 1$ leans Poisson, $p \\to 2$ leans Gamma.\n\n", sep = "")
    for (md_path in md_paths) {
      ind_key <- basename(dirname(md_path))
      ind_label <- industry_labels[ind_key] %||% toupper(ind_key)
      md <- read_csv(md_path, show_col_types = FALSE)

      # Round numeric cols and drop columns that are entirely NA (e.g.
      # tweedie_power for industries with no Tweedie outcome).
      md_clean <- md %>%
        mutate(across(where(is.numeric), ~ round(., 3))) %>%
        select(where(~ !all(is.na(.))))

      cat(sprintf("\n\n## %s\n\n", ind_label))
      cat("\\begin{landscape}\n")
      tbl <- kable(md_clean,
                   format = "latex",
                   booktabs = TRUE,
                   longtable = TRUE,
                   escape = TRUE,
                   caption = sprintf("%s: panel-rate model details by outcome",
                                      ind_label)) %>%
        kable_styling(latex_options = c("hold_position", "repeat_header"),
                      font_size = 10)
      print(tbl)
      cat("\\end{landscape}\n\n")
    }
  }
}
```

# Appendix: Figure Manifest

```{r manifest-table, results='asis'}
cat("\\begin{landscape}\n")
manifest_tbl <- manifest %>%
  select(industry, outcome, component, figure_type, filename) %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    caption = "All figures generated for this report",
    longtable = TRUE
  ) %>%
  kable_styling(
    latex_options = c("hold_position", "repeat_header"),
    font_size = 9
  )
print(manifest_tbl)
cat("\\end{landscape}\n")
```
